---
title: "A Data Science Breakdown: What Ingredients Are You Tasting in Authentic Japanese Flavors?"
author: "Jingsong Gao (jg2109), Yu Kang (yk685), Chao Li (cl1486), Ercong Luo (el890), Rui Qiu (rq47)"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
---

> Note that this `index.html` is just a temporary container to hold our visualizations. Therefore, we did't spend too much time tweaking the embedded html widget styles in the rmarkdown-generated webpage. We've also included links to our original visualizations (all in html format).

## Core Network

This core network visualization shows the relationship between recipes and ingredients. We visualize recipes and ingredients as nodes and the links as edges. Interactive visual elements enable users to explore the network and find many interesting insights and conclusions.

**[Click to view](data_for_viz/01-network/01-network.html).**

```{r, message=FALSE, echo=FALSE}
knitr::include_url("data_for_viz/01-network/01-network.html")
```

## Foreign-origin Dishes in Japanese Cuisine

Our story focuses on answering "what makes Japanese food Japanese", and this visualization gives another perspective to show the influence of foreign cusines on Japanese food. That is to say, the authenticity of a country's dish, although might be defined by its unique set of ingredients, it is still inevitable to ignore external impacts.

**[Click to view](data_for_viz/02-map/02-map.html).**

```{r, message=FALSE, echo=FALSE}
knitr::include_url("data_for_viz/02-map/02-map.html")
```

## Radar Plot of Ingredients

People are wondering what makes Japanese food so special. This radar plot gives an advantage in providing the comparison between different sub-classes recipes. Given an example, as the second radar plot shows, the *blue* radar proves that the Japanese desserts tend to pay more attention to liquid condiments and powder condiments. With the filtering buttons on the right, this plot allows audiences to explore more secrets of the Japanese recipes.

**[Click to view](data_for_viz/03-windrose/windrose.html).**

```{r, message=FALSE, echo=FALSE}
knitr::include_url("data_for_viz/03-windrose/windrose.html")
```

## Beeswarm Plot of Common Nutrients

This beeswarm visualization displays the relative level of 5 main nutrients for the recipes. We treat level of each nutrient of single recipe as nodes and connect nodes of each recipe with eages. The interactive visual elements mainly enable users to hover over nodes to check the relative level of nutrients for a single dish, or click those nodes to display exact nutrition information about the recipe at the corner of plot. Overall, this plot offers a distinct aspect to observe nutritional patterns of recorded recipes.

**[Click to view](data_for_viz/04-beeswarm/04-beeswarm.html).**

```{r, message=FALSE, echo=FALSE}
knitr::include_url("data_for_viz/04-beeswarm/04-beeswarm.html")
```

## The most recurrent ingredients in Japanese entrée recipes

The final visualization included here is an interactive barplot that shows the most recurrent ingredients in Japanese entrée recipes. The custom-labeled ingredient categories `asian`, `common`, and `japanese exclusive` are used to color-code the barplot. We see that the most recurrent ingredients are actually just common ingredients such as sugar and salt, but the green bars of `japanese exclusive` ingredients such as sake and mirin do appear frequently. 

The next step to complete the visualization is to see a correlation between how recurrent an ingredient in Japanese entrée dishes, and how frequently searched these ingredients are. The x-axis of the barplot is sorted according to occurrences so that a plot below can share the same axis, and a reader will be able to clearly see whether the statistical summaries such as average google search rate trends up from left to right just like the top plot. This feature implementation is in progress.

**[Click to view](data_for_viz/05-barplot/05-barplot.html).**

```{r, message=FALSE, echo=FALSE}
knitr::include_url("data_for_viz/05-barplot/05-barplot.html")
```
